Determinism, Complexity, and Predictability in Computer Performance

### 2014-01-06 pecomplexity.tex
fix some spacing
updating table a bit

\author[1]{Joshua Garland \thanks{joshua.garland@colorado.edu}}
\author[1]{Ryan James \thanks{ryan.james@colorado.edu}}
\author[1,2]{Elizabeth Bradley \thanks{lizb@colorado.edu}}
\affil[1]{Department of Computer Science \\
  University of Colorado at Boulder \\
  Colorado, USA
}
\affil[2]{Santa Fe Institute \\
  New Mexico, USA
}

@@

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                  & Horizon & nRMSE LMA           & nRMSE mean          & $l=5$                   & $l=6$                   \\
\hline
gcc               & 4,542   & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ & $0.950991 \pm 0.001073$ & $0.942964 \pm 0.001256$ \\

@@

SVD\_Full         & 22,072  & $0.0323 \pm 0.0019$ & $0.1784 \pm 0.0040$ & $0.876517 \pm 0.004354$ & $0.850805 \pm 0.003454$ \\
SVD\_IPC\_Regime1 & 2,158   & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ & $0.976109 \pm 0.008359$ & $0.957204 \pm 0.015623$ \\
SVD\_IPC\_Regime2 & 6,902   & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ & $0.875984 \pm 0.005161$ & $0.846360 \pm 0.004420$ \\
SVD\_IPC\_Regime3 & 947     & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ & $0.776841 \pm 0.007290$ & $0.715747 \pm 0.005605$ \\
SVD\_IPC\_Regime4 & 2,929   & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ & $0.907348 \pm 0.008018$ & $0.824626 \pm 0.007707$ \\
SVD\_IPC\_Regime5 & 3,255   & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$ & $0.733272 \pm 0.007562$ & $0.677575 \pm 0.006792$ \\
SVD\_IPC\_Regime6 & 5,804   & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ & $0.810087 \pm 0.013468$ & $0.747545 \pm 0.010607$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

>>>>

\author[1]{Joshua Garland \thanks{joshua.garland@colorado.edu}}
\author[1]{Ryan James \thanks{ryan.james@colorado.edu}}
\author[1,2]{Elizabeth Bradley \thanks{lizb@colorado.edu}}
\affil[1]{Department of Computer Science\\
  University of Colorado at Boulder\\
  Colorado, USA
}
\affil[2]{Santa Fe Institute\\
  New Mexico, USA
}

@@

\begin{table}[htdp]
\caption{Average nRMSE over 15 runs for each signal and average wpe at word length 5 and 6 for each signal. }
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
                  & Horizon & nRMSE LMA           & nRMSE na\"{i}ve          & $l=5$                   & $l=6$                   \\
\hline
gcc               & 4,542   & $0.1407 \pm 0.0063$ & $0.1487 \pm 0.0066$ & $0.950991 \pm 0.001073$ & $0.942964 \pm 0.001256$ \\

@@

%SVD\_Full         & 22,072  & $0.0323 \pm 0.0019$ & $0.1784 \pm 0.0040$ & $0.876517 \pm 0.004354$ & $0.850805 \pm 0.003454$ \\
SVD\_IPC\_Regime1 & 2,158   & $0.1680 \pm 0.0317$ & $0.3517 \pm 0.5223$ & $0.976109 \pm 0.008359$ & $0.957204 \pm 0.015623$ \\
SVD\_IPC\_Regime2 & 6,902   & $0.1716 \pm 0.0043$ & $0.1762 \pm 0.0012$ & $0.875984 \pm 0.005161$ & $0.846360 \pm 0.004420$ \\
SVD\_IPC\_Regime3 & 947     & $0.0507 \pm 0.0011$ & $0.5413 \pm 0.0005$ & $0.776841 \pm 0.007290$ & $0.715747 \pm 0.005605$ \\
SVD\_IPC\_Regime4 & 2,929   & $0.1288 \pm 0.0471$ & $0.2308 \pm 0.0867$ & $0.907348 \pm 0.008018$ & $0.824626 \pm 0.007707$ \\
SVD\_IPC\_Regime5 & 3,255   & $0.0235 \pm 0.0022$ & $0.1306 \pm 0.0003$ & $0.733272 \pm 0.007562$ & $0.677575 \pm 0.006792$ \\
SVD\_IPC\_Regime6 & 5,804   & $0.0196 \pm 0.0022$ & $0.0508 \pm 0.0003$ & $0.810087 \pm 0.013468$ & $0.747545 \pm 0.010607$ \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%
